Modelos

### 2019-02-04 20190117_modelos.Rmd
Update 20190117_modelos.Rmd
feb04

   tr <- createTexreg(
       coef.names = names,
       coef = co,
       se = se,
       pvalues = pval,
       gof.names = gof.names,
       gof = gof)
   return(tr)
}
test <- createTexreg
ac <- extract.lmHC2(logOGcov1) #condición A con robust SE 
bc <- extract.lmHC2(logOGcov2) #condición B con robust SE 
cc <- extract.lmHC2(logOGcov3) #condición C con robust SE 
texreg::screenreg(l = c(ac,bc,cc))

>>>>

   tr <- createTexreg(
       coef.names = names,
       coef = co,
       se = se,
       pvalues = pval,
       gof.names = gof.names,
       gof = gof)
   return(tr)
}
test <- createTexreg
ac <- extract.lmHC2(logOGcov1) #condición A con robust SE 
bc <- extract.lmHC2(logOGcov2) #condición B con robust SE 
cc <- extract.lmHC2(logOGcov3) #condición C con robust SE 
texreg::screenreg(l = c(ac,bc,cc)) #TEST
